Body Image and Trikafta

### 2023-05-01 Emily Muther/body_image_trikafta.qmd
ZINB for Emma Lyons

```{r warning=FALSE}
#| include: false
library(tidyverse)
library(gtsummary)
library(kableExtra)
library(foreign)
# Read in data
df = read.spss("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage3.6.23.sav",to.data.frame = T)
# Filter
df = df %>% 
  filter(TakingTrikafta=="yes")
# Trim white space
df = df %>%
  mutate(across(where(is.character),trimws))
# Replace blanks with NA
df[df==""]=NA
```

@@

# Figure

```{r}
# | label: fig-planets
# | fig-cap: Planets

```

>>>>

```{r warning=FALSE}
#| include: false
library(tidyverse)
library(gtsummary)
library(kableExtra)
library(foreign)
library(plotly)
library(pscl)
library(glmnet)
# Read in data
df = read.spss("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage3.6.23.sav",to.data.frame = T)
# Filter
df = df %>% 
  filter(TakingTrikafta=="yes")
# Trim white space
df = df %>%
  mutate(across(where(is.character),trimws))
# Replace blanks with NA
df[df==""]=NA
# Categorical variables
df$FRS_Category = relevel(df$FRS_Category,ref = "neutral")
```

@@

# Mental health scores by FRS category

## PHQ9

### Basic model

Because almost 50% of respondents scored 0 on the PHQ9 and the variance appears to be much larger than the mean, we used a zero-inflated negative binomial (ZINB) model.

```{r}
# Plot all the zeroes
p = ggplot(df,aes(x=PHQ9_Total)) + geom_histogram(binwidth = 1) + theme_bw()
ggplotly(p)
# Fit ZIP model
zinb1 <- zeroinfl(PHQ9_Total ~ FRS_Category,data = df,dist = "negbin")
summary(zinb1)
```

The output above suggests that there are no differences between FRS categories in terms of the likelihood of scoring a 0 on the PHQ9, or in terms of score for those with a non-zero score. Because there may be other variables that predict a score of 0, we used the lasso to find a model for 0 scores. Parameters for the lasso were chosen based on 10-fold cross validation (CV).

```{r}
# Get variables with no missing data, and at least some variance.
x = df[,which(colSums(is.na(df))==0)]
x = x[,-caret::nearZeroVar(x)]
# Remove variables that wouldn't make sense and other mental health variables
x = x %>% select(-c(ID,DOB),-contains("PHQ9"),-contains("GAD7"),
                 -contains("FRS"),-contains("bes"),-PercentAdherence)
preds = colnames(x)
# Outcome
df$PHQ9_0 = as.factor(df$PHQ9_Total==0)
# As a formula
f = as.formula(paste0("PHQ9_0~",paste0(preds,collapse = "+")))
# Lasso
xm = model.matrix(update(f,.~.-1),df)
y = df$PHQ9_0
cvfit = cv.glmnet(xm, y,family="binomial",nlambda=1e6)
# Results
coef(cvfit, s = "lambda.min")
coef(cvfit, s = "lambda.1se")
```

Even with CV on $10^5$ lambda values, no variables are associated with the probability of scoring a 0.

# Questions

1. For the ZINB model, should we use different predictors for the logistic part of the model (i.e., the part that predicts whether someone will have a non-zero score) based on clinical knowledge? For example, would you expect that certain ages would be more likely to score a 0?
